\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{cite}


\newcommand{\signature}[2]{%
	\noindent%
	\textbf{{#1}}\\\\
	\begin{tabular}{@{}p{2.5in}@{}}
		\\ \hline \\[-.75\normalbaselineskip]
		\texttt{{#2}}
	\end{tabular} \hspace{0in}
	\begin{tabular}{@{}p{2.5in}@{}}
		\\ \hline \\[-.75\normalbaselineskip]
		Date
	\end{tabular}\\
}


\title{Master Thesis:\\\Large{Stable communication over a wireless network under
	heavy load}
\\\large{Goal Document for Master's Thesis work\\by}}
\author{Mattias Eklund \& Carl Nilsson Nyman}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}

\pagebreak
\setcounter{page}{1}

\begin{tabular}{lll}
	\textbf{Students:} & Mattias Eklund & Carl Nilsson Nyman \\
	\textbf{Civic reg nbrs:} & 19880116-0071& 19911008-1412\\
	\textbf{Email address:} & \texttt{mat10mek@student.lu.se}
	& \texttt{mat10cni@student.lu.se} \\
	\textbf{Main supervisor:} & TBD & \\
	\textbf{Examiner} & TBD & \\
	\textbf{Project start} & TBD & \\
	\textbf{Project end} & TBD & \\
	\textbf{Course Code} & EITM01 & 
\end{tabular}

%------------------------------------------------------------------------------%
%
%Ett förslag på examensarbete är att designa och implementera ett system för
%trådlös kommunikation mellan Uniti och perifera enheter. Primärt kommer detta
%att användas för kommunikaton mellan bilens infotainment-system och ett
%smartphone-gränssnitt, men kan även användas för att exempelvis låsa bilen med
%en separat enhet. Systemet ska även gärna vara skalbart till fler enheter,
%anpassat för kommunikation med Internet-of-Things (IoT) och Vehicle-to-Vehicle
%(V2V).
%
%Utvärdering och implementering av trådlösa protokoll för denna kommunikation är
%en stor del av arbetet, där även säkerhet är en viktig aspekt. Praktiskt kommer
%detta arbete med stor sannolikhet att integreras med övriga system i Unitis
%prototyp som ska visas upp i slutet av sommaren. För denna demo behöver Uniti
%en stabil och säker trådlös fjärrstyrning av bilen, samt en videolänk från de
%kameror som är monterade på bilen. Eftersom Uniti kör på Robot Operating System
%(ROS), behöver även en brygga implementeras mellan valt nätverksprotokoll och
%ROS. Användargränssnittet kommer att köras i Unity3D och kompatibilitet med
%detta behöver därmed säkerställas.
%
%Utöver detta visar vi gärna upp en lösning för trådlös inloggning och
%synkronisering av användarprofiler mellan en smartphone och bilens
%infotainment-system. Om det finns intresse och tid över så kan projektet enkelt
%utökas till att även inkludera design och implementering av ett
%användargränssnitt för tablets/smartphones i Unity3D.
%
%------------------------------------------------------------------------------%

\section{Introduction}
%Technology advancement in…

%Borde vara mer fokus på att informationsöverföring via trådlösa medier
%Fokus på stabilitet om något, onödigt att diskutera säkerhet för mycket ifall
%vi inte ska gå in på det.

%% 

%The need for secure and stable connection via wireless interfaces has become
%more and more relevant today. Users in a system should be able to trust a
%connections stability and security. By extension companies that supply services
%that depend on wireless connectivity should be able to guarantee stability
%and security in their connections.

When transmitting important data over a wireless connection it is important that
the data arrives in a timely manner. The medias used in a network should meet
all the requirements which the user imposes upon it. A dependency should be
enforced upon all the components in a network to ensure the stability of the
entire network.

%% De här bitarna bör snarare vara i introduktionen

%Wireless communication is allready used in the car industry today, and is used
%for (among other things) updating allready existing software on platforms
%allready in use. This is to ensure that bugs and security flaws in older models
%gets patched out as they are discovered.

%This communication is however not time critical as updates are performed when
%the vehicle is not in use. The communication that Uniti requires for this is
%much more time critical as input from a mobile device will affect the vehicle
%in very close to real time.

\section{Backgound and motivation}
%Recent research in this area…

%Bakgrunden borde vara mer en bakgrund till vårt exjobbs utförande...

%Uniti is a new company that is developing an electric vehicle which is supposed to drive autonomously. 
%For this purpose Uniti has expressed the need for a stable
%wireless communication link between their vehicle and peripheral devices, such
%as a tablet or laptop.

Uniti is a newly founded company that is developing an electric vehicle which will be driven autonomously.
In a couple of months Uniti will showcase their advancements in their development,
by hosting a demostrational event with their car in front of thousands of participants.
During this event the development of their car is not supposed to be finished, 
but rather supposed to be far along enough to showcase its electric-only propulsion and autonomous features. 

Today Uniti uses a UDP stream for communication between the vehicle and
peripheral devices, this is not really ideal as UDP-applications most likely
suffer from package-loss, errors, or duplication. This is fine for some
applications but for some applications it could be critical to miss out on certain information. Furthermore it is also desireable to use a protocol which is designed with, the application of the data which is transferred, in mind.

Uniti has expressed the need for a better solution for communicating with the vehicle.
This solution is supposed to let the vehicle be both monitored and in worst case controlled via outside devices.

%Using TCP will provide ordered and error-checked delivery of data, however, the
%application might have to wait for retransmission of packages. This approach is
%not ideal as latency might cause issues when controlling the vehicle.

%Furthermore, the media over which the communication is transmitted needs to be
%taken into consideration. Depending on the location, WiFi might not be
%available or stable enough. In such cases, could 4G be used instead? Or is 4G
%reliable enough to be used exclusively for this purpose? Reliable is in this
%case refering to low latency and low package loss.
%

\section{Project aims and challenges}
%The aim with this Master’s thesis work is to… To find a feasible solution to
%these questions are challenging…

%Det borde vara mer direkt på vad vi ska göra här och vad vill vi uppnå
%Vilka mål det finns att uppnå och dess begränsningar.

The goal of the thesis is to evaluate a couple of different mediums of wireless
network transmission to and from Uniti's vehicle, as well as evaluating a couple
of different protocols for sending both video data and more discrete signals as
in Start or Stop.

For our thesis we will be investigating the compatibility of setting up this
connection both with 4G and WiFi Transmission. Furthermore we will also look
into implementing both Real-time Transport Protocol (RTP) and Real-time
Messaging Protocol (RTMP) for sending video data. 

We will also look into implementing a connection for the discrete control
signals using either Stream Control Transmission Protocol (SCTP) or Multipath
Transmission Control Protocol (MPTCP), to ensure that the time critical control
signals reach the vehicle within a desiered time. This results in eight cases
that we are going to be investigate.

Uniti has in turn set the requirements on our solution that it is supposed to
work in an environment with at least 10000 people and at most 20000. Our
transmission of discrete signals has to be guaranteed to arrive with a
worst-case latency of 50ms. Finally video transmission should work with an
average latency of around 100ms.
 

%The goal of this thesis is to evaluate different mediums of wireless network
%transmission to and from a unit in motion. This includes implementing a wireless
%connection between the unit and different peripheral devices. This work involves
%certain research into different network protocols and wireless technologies such
%as 4G or WiFi.

%The focus of the work will be to find a solution which results in a long range
%transmission with minimal latency and a minimal rate of packet-loss.

%The aim with this Master's thesis work is to research and implement a stable
%connection between Uniti's car and peripheral devices such as a telephone or
%laptop via wireless connection such as WiFi, 4G, or Bluetooth.

%This connection should be able act with an acceptable latency and with a minimal
%rate of packet-loss.

%The goal within this work is to research and conclude what the best media (4G,
%Wifi etc.) and the best format (network protocol etc.)


%The problems lies in ensuring that the connection remains stable on
%networks that are under heavy load while not contributing too much to the
%latency of the connection. Setting up the connection and making it secure 
%is also of great concern but our aim within this project has its focus 
%set on ensuring low latency and stability between units.

\section{Approach and methodology}
%The thesis project will be based on…
%Hur ska vi göra exjobbet och i vilka steg tar vi det?

%Detta borde snarare handla om hur vi först gör detta och sedan gör detta.

Our thesis project will be executed through a couple of steps.

During the first stage we will work on a rough implementation of our connection
using the rosbridge package to communicate with the Robot Operating System
(ROS). ROS is the operating system which drives the core functionality of the 
Vehicle. At this stage we will implement the remaining part of the connection
using basic protocols over WiFi.

The second stage of our project will be focused on making our implementation 
work using the different protocols specified. This will probably be our most 
time-consuming stage as not all the protocols have native support for Linux and
rosbridge.

The third stage of our project is centered around making sure the connection 
works well over both the Wi-Fi Setup and the 4G Setup.

The final stage is the evaluation step where we will use the larger test module
to simulate heavy loads on the network to generate test data. The test data is
then used to deduce which solution is best suited for the constraints set upon
the project by Uniti.

%The majority of our thesis project will be put into implementing a wireless
%connection between Uniti's vehicle and a test platform which will help us
%evaluate our thesis.

%The first part of our thesis project will be put into implementing a connection
%with the platform which their vehicle uses (Robot operating system), which will
%be implemented through the use of the package rosbridge.

%Beyond this we will be able to implement a connection from the vehicle to a test
%platform through more conventional means.

%Finally we will be able to substitute the different factors in our connection,
%such as medium and protocol, from the vehicle to the test platform with
%different mediums and protocols to test our thesis and in that achieve the goal
%we set.

%The thesis project will be based on the requirements set by the different parts
%of the company Uniti's infrastructural software. This software is based
%partially in their car which uses Robot Operating System (ROS) but also in
%their cell phone application which is built in Unity3D. Most of this project
%will include implementing a network link between these parts. Uniti has
%already started looking at developing some kind of link, which is what
%we will initially work with to build upon.


\section{Previous work}
%Back-ground knowledge and experiences can be found among the professors and PhD
%students at the department…

%Tidigare arbete inom området ska mer röra information vi behöver utifrån för
%att göra vårt exjobb Detta är det sista man skriver i rapporten och man behöver
%nog inte läsa artiklar djupare än att veta vad man kan ta ifrån dem.
%Det är här t.ex. orimligt att använda Wi-Fi för att tänk på vad som händer när
%man kör ifrån en accesspunkt

The main field of this thesis is latency and response time and there are quite a
lot of mechanisms and methods specifically for the measurement of both. These
could be used in chain and used to calculate the latency of the video stream.

The protocols that are to be used have allready been specified in their
respective specification.

\subsection*{RTP: Real-time Transport Protocol}	
Real-time Transport Protocol has a history as one of the more popular protocols
for media streaming. It is one of the most well-documented application layer
protocols. \cite{spec_RTP}

\subsection{RTMP: Real-time Messaging Protocol}
RTMP is n extension on RTP that mainly improves on latency and has support on
most plattforms. This protocol seems to specify itself in areas that are
benificial to this project. \cite{spec_RTMP}

\subsection{MPTCP: Multipath TCP}
MPTCP is an experimental improvent of TCP allowing for multiple ip-adresses and
high transfer rate. This will be useful in the case where	WiFi and 4G connection
is available. \cite{spec_MPTCP}

\subsection{SCTP: Stream Control Transport Protocol}
SCTP is a protocol that is message based like UDP, and ensures reliable,
in-sequence transport of message with congestion control like TCP.
\cite{spec_SCTP}

The work that we will be doing will be placed within a ROS node and integrated
with Uniti's vehicle. As they have been working with ROS and ROS nodes they can
supply direct help with installation and development issues. The ROS community
is also quite active and should be able to provide support.


%We have read an article \cite{NIST_report} concerning more general
%internet security on both the link layer and application layer and
%it have broght up some interesting points concerning both security and
%stability. Mostly concerning what aspects you have to consider when specifying a
%network group.

%According to Giuseppe's analysis of IEEE 802.11 performance
%\cite{PAIEEE_article}, the performance is, not very suprisingly, affected by the
%number of units on the network. This will be an issue during showcasing of
%Uniti's vehicle as low latency is a requirement for safe remote operation of the
%vehicle as during showcasing the network will most likely be heavily populated
%by devices.

%These articles went into some detail about the 802.11 standard for Wifi.
%We intend to start our thesis project by testing to use 802.11 for our 
%wireless communication setup.


\section{Advancements and Outcome}
%Verification of the theoretical knowledge will be shown by real-world
%experiments… A scientific conference paper can be expected…

%Vad har vi åstadkommit i vårt arbete, vad är det tekniska eller
%forskningsrelaterade vi har tagit fram som inte tidigare fanns?


% --- DRAFT FOR ADVANCEMENTS AND OUTCOME --- %

The outcome from this thesis work is made up of two parts, implementation and
the test results.

The implementation will be the final ROS node that we deem most suitable based
on the test results.

The test-results from the different implementations of the connection between
Uniti's vehicle and peripheral devices could be used as a basis for decisions
regarding implementation of similar wireless application and which protocol
and connection media that should be used.

% ---------------- END DRAFT --------------- %

The theoretical knowledge used within this project will be rather easy
to verify the success of, seeing as the implementation of the different 
protocols and integration with different wireless medias will provide
feedback easily. Something that is harder to verify by oneself is whether
or not a certain solution is safe in terms of network security or whether
or not it is stable under heavy loads, as these things require larger
experiments to verify.

\section{Resources}
%Linux based workstations, placed in thesis workers rooms, will be
%available for simulation and implementation.

%Vilka resurser finns tillgängliga till oss när vi gör vårt exjobb.

We will work with our thesis at Uniti's office in Lund where Uniti will provide
us with the resources necessary to complete this thesis work. Below is a list of
agreed upon resources that will be provided.

\begin{itemize}
	\item[Workstations] Stationary computers to work on.
	\item[Laptop] Just like a stationary computer this will be used to produce
		code on.
	\item[Test platforms] Uniti provides two test platforms that will be available
		during the course of the master thesis work. One full size test platform
		(denoted as \texttt{Mule}) and one small size test platform (denoted as
		\texttt{Robot})
		\begin{itemize}
			\item[\texttt{Robot}] The small size test platform. This will run the same
				ROS-core as the real product on weaker hardware and will allways be
				available for use by us, so no planning and coordination with the rest
				of the team at Uniti is needed. Some parameters may need to be tweaked
				before moving to full size testing, but the general functionallity will
				not be affected by the size difference in our case.
			\item[\texttt{Mule}] The full size test platform. This will run on
				hardware that will be very similar or equal to the hardware that will be
				present in the vehicle at the demo. The rest of the team at Uniti will
				be working and testing on this platform during the course of the master
				thesis work so some planning and coordination with the rest of the team
				will be necessary to be able to perform the tests on the full size
				model. This should however not be to much of a problem as most of the
				testing can be done on the small size test platform.
		\end{itemize}
	\item[TOBY-L210] Long range radio module. 4G with 3G/2G fallback.
	\item[EMMY-w163] Short range radio module. WiFi.
	\item[EVK-L2x] Evaluation kit for TOBY-L2x
	\item[EVK-EMMY-W1] Evaluation kit for EMMY-w1x
	\item[source code] Current source code.

\end{itemize}

During our thesis work, we will work by integrating our ideas into Uniti's
current source code.
Network tests and simulations will be performed with the help of Uniti's
equipment.



\bibliography{goal_doc.bib}{}
\bibliographystyle{plain}


This Goal Document is approved by:\\\\\\\\

\signature{Uniti supervisor}{Kritofer Jansson}\\

\signature{Main supervisor}{<name here>}\\

\signature{Examiner}{<name here>}

\end{document}
